\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research

### 2025-03-09 paper.tex
added text

\begin{center}
    \includegraphics[width=0.8\textwidth]{min_cut_graph.pdf}
\end{center}

>>>>

\begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
    \centering
    \includegraphics[width=0.6\textwidth, height=0.23\textheight]{mincut_graph.jpeg}  % Adjust width as needed
    \caption{5 atomic region weighted undirected graph model of the bulk. Where each subregion is cutting deeper into the bulk. Each subregion is a minimal surface (RT surface) and is connected by the min-cut (red) line.}  % Caption text
    \label{fig:mincut}  % Label for referencing
\end{figure}
